---
title: "bootstrapping"
author: "Fang Liu"
date: "11/23/2021"
output: html_document
---

```{r}
library(tidyverse)
library(p8105.datasets)
library(modelr)

set.seed(1)
```

Would you use bootstrapping with cross-validation! 
Bootstrapping is for inference on model parameters... 
```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```

Make a plot
```{r}
sim_df_nonconst %>% 
  ggplot(aes(x = x, y = y)) + geom_point()
```
Note that the assumption of constant varaince is violated... thus, can't use normal statistics 

```{r}
sim_df_nonconst %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()
```

How do we get better standard errors? bootstrapping!
```{r}
bootstrap_sample = 
sim_df_nonconst %>% 
  sample_frac(size = 1, replace = TRUE) %>% 
  arrange(x)

lm(y~x, data = bootstrap_sample)
```

Let's write a function
```{r}
boot_sample = function(df) {
  sample_frac(df, size = 1, replace = TRUE)
}
```

Now, we'll make a tibble to keep track of everything. 
```{r}
boot_strap_df = 
  tibble(
    strap_number = 1:1000,
    strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
  )
```

```{r}
boot_strap_df %>% 
  mutate(
    strap_sample = map(strap_sample, ~arrange(.x, x)))
```


```{r}
bootstrap_results %>% 
  ggplot(aes(x = estimate)) + 
  geom_histogram() + 
  facet_grid(~term, scales = "free")

lm(y ~ x, data = sim_df_nonconst) %>% 
  broom::tidy()

bootstrap_results %>% 
  group_by(term) %>% 
  summarize(
    se = sd(estimate)
  )
```
The bootstrapping is probably the more "accurate" one because assumption of equal variance is NOT required! 
## Use model r  
```{r}
sim_df_nonconst %>% 
  bootstrap(n = 1000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap), ~lm(y ~ x, data =.x)),
    results = map(models, broom::tidy)
)
```

## airbnb
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location /2 ) %>% 
  rename(
    borough = neighbourhood_group
  ) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, room_type)
```

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point()
```

```{r}
airbnb_bootstrap_results = 
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  bootstrap(n = 100, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(price ~ stars, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)

#more filtering
airbnb_bootstrap_results %>% 
  filter(term == "stars") %>% 
  ggplot(aes(estimate)) + 
  geom_density()

ggp_star_est = 
  airbnb_bootstrap_results %>% 
  filter(term == "stars") %>% 
  ggplot(aes(estimate)) +
  geom_density()

ggp_scatter = 
  nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point()

#put the two graphs together using 'patchwork' library
library(patchwork)
ggp_star_est + ggp_scatter
  
```







