---
title: "linear_models"
author: "Fang Liu"
date: "11/16/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

Load NYC airbnb data.
```{r}
data("nyc_airbnb")

nyc_airbnb =
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group
  ) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighbourhood, room_type)
  
```

Visualizations 
```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) + 
  geom_point()
```
Note the violation of equal variance across x... you can see that there is more spread with increasing stars...

Let's fit a linear model...
```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

Let's look at this...
```{r}
fit #simple output
summary(fit) #more stuff such as t values and p-values 
summary(fit)$coef

fit %>% broom::tidy()
```

If you want to present output..
```{r}
fit %>% 
  broom::tidy() %>% 
  mutate(term = str_replace(term, "borough", "Borough: ")) %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
#creates dataframe :) 
```

## Diagnostics  
```{r}
resid(fit)
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = resid)) + 
  geom_density() + 
  xlim(-200, 200)
```


## Interactions?  
Price depends on stars, and maybe room type... WITHOUT interaction terms...
```{r}
fit = lm(price ~ stars + room_type, data = nyc_airbnb)

broom::tidy(fit)

```

With interactions terms
```{r}
fit = lm(price ~ stars*borough + room_type*borough, data = nyc_airbnb)

broom::tidy(fit)
```

HOWEVER, when we have too many boroughs or groups...Lets try nesting
```{r}
nyc_airbnb %>% 
  relocate(borough) %>% 
  nest(data = price:room_type) %>% 
  mutate(
    lm_fits = map(.x = data, -lm(price ~ stars + room_type, data = .x)),
    lm_results = map(lm_fits, broom::tidy)
  ) %>% 
  select(borough, lm_results) %>% 
  unnest(lm_results) %>% 
  filter(term == "stars")
```

Neighborhoods in Manhattan 
```{r}
manhattan_lm_results_df = 
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  select(-borough) %>% 
  relocate(neighbourhood) %>% 
  nest(data = price:room_type) %>% 
  mutate(
    lm_fits = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    lm_results = map(lm_fits, broom::tidy)
  ) %>% 
  select(neighbourhood, lm_results) %>% 
  unnest(lm_results)
```

```{r}
manhattan_lm_results_df %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighbourhood, y = estimate)) +
  geom_point() +
  facet_grid(~term) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Entire --> private room (-$100)
Entire home --> shared room (-$100+) 
**Save more by having a shared room! 
Stars doesn't matter that much except in a couple places~ 

## Logistic regression 
```{r}
nyc_airbnb =
  nyc_airbnb %>% 
  mutate(
    expensive_apt = as.numeric(price > 500) #creates binary outcome 
  )
```

Let's fit a logistic regression for the binary outcome.
```{r}
logistic_fit = 
  glm(
    expensive_apt ~ stars + borough,
    data = nyc_airbnb,
    family = binomial())

logistic_fit %>% broom::tidy() %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: "),
    estimate = exp(estimate)
  ) %>% 
  select(term, OR = estimate, p.value)

nyc_airbnb %>% 
  modelr::add_predictions(logistic_fit) %>% 
  mutate(pred = boot::inv.logit(pred))
#gives us the probability of being 0 or 1 (i.e., expensive apartment or not)
```

> binomial()
Family: binomial
Link function: logit 

> poisson()
Family: poisson
Link function: log

>family() 
give us different families that are available! 
